---
title: "Capstone Project - Mercari Price Predictor"
author: "Ram Subramaniam"
date: "February 22, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Mercari is a Japanese community powered shopping app. It gives an opportunity for people to sell their stuff - new or used. It is always challenging for anyone to set a fair price for the item they are trying to sell. This is contest currently active in Kaggle and it is for developers/enthusiasts to build a tool that will predict the price of an item(s) that people are trying to sell accurately.

## Problem Statement

As people try to sell their good(s) in Mercari website, there needs to be a effective tool to predict the price based on characteristics of the item as enteredd by the seller. The characteristics entered by the seller are as follows

1. Short Item Description
2. Product Category
3. Detailed Description
4. Item Condition 
5. Brand Name
6. Shipping (paid by seller or buyer)

## Tragetted Users

The users who will use this will be sellers of products using Mercari app.

## Data

As part of the Kaggle contest the data was provided to the contestants by Mercari. The data is located here

Datasets - [Mercari Datasets](https://www.kaggle.com/c/mercari-price-suggestion-challenge/data) 

The above link contains datasets for both Train and Test. The data structure of the train and test datasets are as below:

* test_id and train_id - the id of the listing
* name - the title of the listing. 
* item_condition_id - the condition of the item provided by the seller
* category_name - category of the listing
* brand_name - brand name of the item being sold
* price - the price that the item was sold for. This is the target variable that you will predict. The unit is USD. This column doesn't exist in test.tsv since that is what you will predict.
* shipping - 1 if shipping is paid for by the seller else 0 if by buyer
* item_description - description of the item

## The Approach

THe folllowing steps highlight the strategy adopted for carrying out analysis

1. Data Wrangling and Cleaning
  * Deal with missing values
  * Dropping of combining columns 
  * Rearrange and transform dataset for cleaner analysis
  * Removing Stop words from the descriptions
2. Exploratory Analysis
  * Grouping items based on price
  * Classification using Latent Dirichlet Allocation model
3. Predictive Analysis
  * Modeling the sample using XGBOOST and Root Mean Square Log Error
  * Tuning the Model
  * Testing out whether the outcome - predicting the price is accurate
    


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r train, echo=FALSE}
library(data.table)
train <- fread("C://Users/rsubra02/Documents/Mercari/train.tsv")
str(train)
#summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
